**Course Project - Part 1**
==========================================
Created by Eduardo Ferreira - 2014


Simulation

In Part 1 of the Course Project, the exponential distribution is simulated. The rate parameter, lambda,for the simulation is 0.2 The simulation investigates the distribution of 40 exponentials.

The function 'rexp' is run 10,000 times, with each simulation producing 40 exponentials and a lambda of 0.2. 2 vectors are created of these simulations: the mean of the 40 exponentials and the standard deviation of the 40 exponentionals.

```{r}
sim_m <- vector()
sim_sd <- vector()
set.seed(5)
for (i in 1:10000) {
  sim_m[i] <- mean(rexp(40, 0.2))
  sim_sd[i] <- sd(rexp(40,0.2))
}
```

**Center of Distribution**

A histogram of the mean values of the simulations shows that it is centered around 5.

```{r}
hist(sim_m, xaxt ='n')
axis(side = 1, at=seq(0,10,1), labels=seq(0,10,1))
```

The theoretical center is determined by 1/lamdba. The center of the distribution of the simulation can be determined by taking the mean of the simulated means.

```{r}
1/0.2
```

And the mean:

```{r}
mean(sim_m)
```

Both of these are 5.

**Variance of the Distribution**

A histogram of the standard deviation values of the simulations shows that it is also centered around 5.


```{r}
hist(sim_sd, xaxt ='n')
axis(side = 1, at=seq(0,10,1), labels=seq(0,10,1))
```

The theoretical standard deviation is determined by 1/lamdba. The center of the distribution of standard deviations of the simulation can be determined by taking the mean of the simulated standard deviations.

```{r}
1/0.2
```
And the mean:

```{r}
mean(sim_m)
```


Both of these are 5.

**Normal Distribution**

For a normal distrubtion with a mean of 5 and sd of 5,

```{r}
norm95 <- qnorm(.95, 5, 5)
```
13.2243 is the 95th percentile.
For our simulated data,

```{r}
sim95 <- qnorm(.95, mean(sim_m), mean(sim_sd))
```
13.0716 is the 95th percentile. The simulation appears to be normally distributed.

**Confidence interval**

```{r}
ci <- mean(sim_m) + c(-1,1)*1.96*(mean(sim_sd)/sqrt(10000))
```

The 95% Confidence Interval is [4.9127, 5.1048]